In this chapter, we construct the ambient environment inside which our model will reside.
To do this, we will set up various pieces of abstract machinery that will help us later.
Some mathematical background not already in mathlib will be included in \cref{c:auxiliary}.

\section{Conventions}
\begin{itemize}
  \item We are working in Lean's type theory, so cardinals and ordinals are quotients of a large type.
  In particular, cardinals are not just specific ordinals, and types cannot be ordinals.
  \item We write \( \#\tau \) for the cardinality of a type \( \tau \).
  \item If \( \tau \) is a type endowed with a well-order \( < \), we write \( \ot(\tau) \) for the order type of \( \tau \) with this well-ordering.
  \item The initial ordinal corresponding to a cardinal \( c \) is denoted \( \ord(c) \).
  The cofinality of an ordinal \( o \) is \( \cof(o) \), and this is a cardinal.
  \item The symmetric difference of two sets is denoted \( s \symmdiff t \coloneq (s \setminus t) \cup (t \setminus s) \).
  Note that \( (s \symmdiff t) \cup (s \cap t) = s \cup t \), and the union on the left-hand side is disjoint.
  \item We use \( f[s] \) for the direct image \( \{ f(x) \mid x \in s \} \). We write \( f^{-1}[s] \) for the inverse image \( \{ x \mid f(x) \in s \} \), and \( f^{-1}(x) \) for the fibre \( \{ y \mid f(y) = x \} \).
  \item For any type \( \alpha \), we write \( \Part \alpha \) for the type \( \sum_{p : \Prop} (p \to \alpha) \).
\end{itemize}

\section{Model parameters}
\begin{definition}[model parameters]
  \label{def:Params}
  \lean{ConNF.Params}
  \leanok
  A collection of \emph{model parameters} is a tuple \( (\lambda, {<_\lambda}, \kappa, \mu) \) such that
  \begin{itemize}
    \item \( {<} = {<_\lambda} \) is a well-order on \( \lambda \), and under this ordering, \( \lambda \) has no maximal element (so \( \ot(\lambda) \) is a limit ordinal);
    \item \( \#\kappa \) is uncountable and regular;
    \item \( \#\mu \) is a strong limit, and satisfies
    \[ \#\kappa < \#\mu;\quad \#\kappa \leq \cof(\ord(\#\mu));\quad \ot(\lambda) \leq \ord(\cof(\ord(\#\mu))) \]
    so in particular, \( \ot(\lambda) \leq \ord(\#\mu) \).
    Note that the inequalities in \( \kappa \) are inequalities of cardinals; the inequality in \( \lambda \) is an inequality of ordinals.
  \end{itemize}
  Given a collection of model parameters, we define
  \begin{itemize}
    \item canonical well-orders on \( \kappa \) and \( \mu \) such that \( \ot(\kappa) = \ord(\#\kappa) \) and \( \ot(\mu) = \ord(\#\mu) \); and
    \item a canonical left-cancellative additive monoid on \( \kappa \), obtained by passing through the equivalence \( \kappa \simeq \{ o : \Ord \mid o < \ord(\#\kappa) \} \).
  \end{itemize}
\end{definition}
\begin{proposition}
  \uses{def:Params}
  \label{prop:Params.minimal}
  \lean{ConNF.minimalParams,ConNF.inaccessibleParams}
  \leanok
  The tuple \( (\mathbb N, {<_{\mathbb N}}, \aleph_1, \beth_{\omega_1}) \) is a collection of model parameters, where the symbols \( \aleph_1 \) and \( \beth_{\omega_1} \) represent particular types of that cardinality.
\end{proposition}
\begin{proof}
  \leanok
  Direct.
\end{proof}
\begin{definition}[type index]
  \label{def:TypeIndex}
  \uses{def:Params}
  \lean{ConNF.TypeIndex}
  \leanok
  The type of \emph{type indices} is \( \lambda^\bot \coloneq \texttt{WithBot}(\lambda) \): the collection of \emph{proper type indices} \( \lambda \) together with a designated symbol \( \bot \) which is smaller than all proper type indices.
  Note that \( \ot(\lambda^\bot) = \ot(\lambda) \), and hence that for each \( \alpha : \lambda^\bot \),
  \[ \#\{ \beta : \lambda^\bot \mid \beta < \alpha \} \leq \#\{ \beta : \lambda^\bot \mid \beta \leq \alpha \} < \cof(\ord(\#\mu)) \]
\end{definition}
\begin{definition}[small]
  \label{def:Small}
  \uses{def:Params}
  \lean{ConNF.Small}
  \leanok
  A set \( s : \Set(\tau) \) is called \emph{small} if \( \#s < \#\kappa \).
  Smallness is stable under subset, intersection, small-indexed unions, symmetric difference, direct image, injective preimage, and many other operations (each of which should be its own lemma when formalised).
  Sets \( s, t : \Set(\tau) \) are called \emph{near} if \( s \symmdiff t \) is small; in this case, we write \( s \near t \).
  Nearness is an equivalence relation.
  If \( s \near t \) and \( u \) is small, then \( s \near (t \mathbin{\diamond} u) \), where \( \diamond \) is one of \( \cup, \cap, \setminus, \symmdiff \).
\end{definition}
\begin{definition}[litter]
  \label{def:Litter}
  \uses{def:Params}
  \lean{ConNF.Litter}
  \leanok
  A \emph{litter} is a triple \( L = (\nu, \beta, \gamma) : \mu \times \lambda^\bot \times \lambda \) where \( \beta \neq \gamma \).
  The type of all litters is denoted \( \Litter \), and \( \#\Litter = \#\mu \).
\end{definition}
\begin{definition}[atom]
  \label{def:Atom}
  \uses{def:Litter}
  \lean{ConNF.Atom}
  \leanok
  An \emph{atom} is a pair \( a = (L, i) : \Litter \times \kappa \).\footnote{This should be formalised as a structure, not as a definition. We should not use the projections of atoms unless absolutely necessary.}
  The type of all atoms is denoted \( \Atom \), and \( \#\Atom = \#\mu \).
  We write \( (-)^\circ : \Atom \to \Litter \) for the operation \( (L, i) \mapsto L \).\footnote{This must be a notation typeclass.}
  We write \( \LS(L) \coloneq \{ a \mid a^\circ = L \} \) for the \emph{litter set} of \( L \).\footnote{Maybe revise this name?}
\end{definition}
\begin{definition}[near-litter]
  \label{def:NearLitter}
  \uses{def:Litter,def:Atom}
  \lean{ConNF.NearLitter}
  \leanok
  A \emph{near-litter} is a pair \( N = (L, s) : \Litter \times \Set \Atom \) such that \( s \near \LS(L) \).\footnote{Like with atoms, this should be a structure. We should create an actual constructor, rather than using the \( \langle - \rangle \) syntax.}
  We write \( (-)^\circ : \NearLitter \to \Litter \) for the operation \( (L, s) \mapsto L \).
  We write \( a \in N \) for \( a \in s \), where \( N = (L, s) \).
  Near-litters satisfy extensionality: there is at most one choice of \( L \) for each \( s \).
  Each near-litter has size \( \#\kappa \) when treated as a set of atoms.
  The type of all near-litters is denoted \( \NearLitter \), and \( \#\NearLitter = \#\mu \) (there are \( \#\mu \) litters, and \( \#\mu \) small sets of atoms by \cref{prop:card_subset_card_lt_cof}; the latter observation should be its own lemma).

  We have \( M \near N \) if and only if \( M^\circ = N^\circ \).
  If \( M^\circ = N^\circ \), then \( M \symmdiff N \) is small and \( M \cap N \) has size \( \#\kappa \).
  If \( M^\circ \neq N^\circ \), then \( M \cap N \) has size \( \#\kappa \) and \( M \cap N \) is small.
\end{definition}
\begin{definition}[base permutation]
  \label{def:BasePerm}
  \uses{def:Atom,def:Litter,def:NearLitter}
  \lean{ConNF.BasePerm}
  \leanok
  A \emph{base permutation} is a pair \( \pi = (\pi^\Atom, \pi^\Litter) \), where \( \pi^\Atom \) is a permutation \( \Atom \simeq \Atom \) and \( \pi^\Litter \) is a permutation \( \Litter \simeq \Litter \), such that
  \[ \pi^\Atom[\LS(L)] \near \LS(\pi^\Litter(L)) \]
  Base permutations have a natural group structure, they act on atoms by \( \pi^\Atom \), they act on litters by \( \pi^\Litter \), and they act on near-litters by\footnote{We need to emphasise these properties, rather than emphasising the real definition \( \pi(N) = (\pi(N^\circ), \pi[N]) \).}
  \[ \pi(N)^\circ = \pi(N^\circ);\quad a \in \pi(N) \leftrightarrow a \in \pi[N] \]
  Base permutations are determined by their action on atoms.
  We should avoid directly referencing \( \pi^\Atom \) and \( \pi^\Litter \) whenever possible.
\end{definition}

\section{The structural hierarchy}

We will now establish the hierarchy of types that our model will be built inside.

\begin{definition}[path]
  \label{def:Path}
  \uses{def:TypeIndex}
  \lean{ConNF.Path}
  \leanok
  If \( \alpha, \beta \) are type indices, then a \emph{path} \( \alpha \tpath \beta \) is given by the constructors
  \begin{itemize}
    \item \( \newoperator{nil} : \alpha \tpath \alpha \);
    \item \( \newoperator{cons} : (\alpha \tpath \beta) \to (\gamma < \beta) \to (\alpha \tpath \gamma) \).
  \end{itemize}
  We define by recursion a \( \newoperator{snoc} \) operation on the top of paths.
  We also prove the induction principle for \( \newoperator{nil} \) and \( \newoperator{snoc} \).

  A path \( \alpha \tpath \bot \) is called an \emph{\( \alpha \)-extended index}.
  We write \( \nil(\alpha) \) for the path \( \{ \alpha \} : \alpha \tpath \alpha \).
  If \( h \) is a proof of \( \beta < \alpha \), we write \( \single(h) \) for the path \( \{ \alpha, \beta \} : \alpha \tpath \beta \).

  We have the inequality
  \begin{align*}
    \#(\alpha \tpath \beta)
    &\leq (\#\{ \gamma : \lambda^\bot \mid \gamma \leq \alpha \})^{<\omega} \\
    &= \max(\aleph_0, \#\{ \gamma : \lambda^\bot \mid \gamma \leq \alpha \}) \\
    &< \cof(\ord(\#\mu))
  \end{align*}
\end{definition}

Many of the objects in this construction have an associated type level \( \alpha : \lambda^\bot \), and by application of a path of the form \( \alpha \tpath \beta \) or \( \beta \tpath \alpha \), we can often define a new object of type level \( \beta \).
For this common task, we register the following notation typeclasses.
\begin{itemize}
  \item \( x \Downarrow A \) is the \emph{derivative} of an object of type \( \beta \) along a path \( A : \beta \tpath \gamma \), giving an object of type \( \gamma \);
  \item \( x \downarrow h \) abbreviates \( x \Downarrow \single(h) \);\footnote{In practice the typeclasses will probably not formally depend on each other, and this `abbreviation' may not be a definitional equality.}
  \item \( x \underset{\bot}{\Downarrow} A \) is the \emph{base derivative} of an object of type \( \beta \) along a path \( A : \beta \tpath \bot \);
  \item \( x \underset{\bot}{\downarrow} \) abbreviates \( x \underset{\bot}{\Downarrow} \single(h) \) where \( h \) is the canonical proof of \( \bot < \beta \) whenever \( \beta : \lambda \);
  \item \( x \Uparrow A \) is the \emph{coderivative} of an object of type \( \beta \) along a path \( A : \alpha \tpath \beta \), giving an object of type \( \alpha \);
  \item \( x \uparrow h \) abbreviates \( x \Uparrow \single(h) \).
\end{itemize}

When we say that an object has an associated type level in this context, we mean that the notation typeclass is registered in the following form.

\begin{verbatim}
class Derivative (X : Type _) (Y : outParam (Type _))
    (β : outParam TypeIndex) (γ : TypeIndex) where
  deriv : X → Path β γ → Y
\end{verbatim}

This means that when inferring the type of the expression \( x \Downarrow A \), we first compute the type of \( x \), which gives rise to a unique type index \( \beta \), then the type of \( A \) is inferred to give \( \gamma \), then the output type \( Y \) is uniquely determined.

The reason that we distinguish \( \underset{\bot}{\Downarrow} \) from \( \Downarrow \) is that the associated type \( Y \) is allowed to differ between the two forms.
We will give a brief example motivated by a definition we are about to make.
For each type index \( \beta \), there is a type of \( \beta \)-structural permutation, comprised of many base permutations.
If we have a path \( \beta \tpath \gamma \), we can convert a \( \beta \)-structural permutation into a \( \gamma \)-structural permutation; this will be the derivative map.
We will see that a given \( \bot \)-structural permutation contains exactly one base permutation, and so the types are in canonical isomorphism.
If \( x \) is a \( \beta \)-structural permutation and \( A : \beta \tpath \bot \), then \( x \Downarrow A \) is a \( \bot \)-structural permutation, and \( x \underset{\bot}{\Downarrow} A \) is the corresponding base permutation.

Because \( \uparrow, \downarrow \) and others are already used by Lean, we use slightly different notation in practice (e.g.\ \( \nearrow, \searrow \)).
In this writeup, however, we will use subscripts for derivatives and superscripts for coderivatives.
We will not distinguish typographically here between the single- and double-struck variants, or between \( \Downarrow \) and \( \underset{\bot}{\Downarrow} \); in the latter case, the syntax \( x_A \) always means \( x \underset{\bot}{\Downarrow} A \) whenever \( A \) has minimal element \( \bot \).
We will also use \( x_\gamma \) to denote the derivative \( x_h \) where \( h \) is some proof of \( \gamma < \beta \), and use \( x^\alpha \) to denote \( x^h \) where \( h : \beta < \alpha \).

\begin{definition-no-bp}[derivatives of paths]
  If \( A : \alpha \tpath \beta \) and \( B : \beta \tpath \gamma \), the derivative \( A_B \) is defined to be the union \( A \cup B : \alpha \tpath \gamma \), and the coderivative \( B^A \) is defined to be \( A_B \).
\end{definition-no-bp}

\begin{definition}[tree]
  \label{def:Tree}
  \uses{def:Path}
  \lean{ConNF.Tree}
  \leanok
  Let \( \tau \) be any type, and let \( \alpha \) be a type index.
  An \emph{\( \alpha \)-tree of \( \tau \)} is a function \( t \) that maps each \( \alpha \)-extended index \( A \) to an object \( t_A : \tau \); this defines its base derivatives.
  The type of \( \bot \)-trees of \( \tau \) is canonically isomorphic to \( \tau \).
  If \( t \) is an \( \alpha \)-tree and \( A : \alpha \tpath \beta \), we define the derivative \( t_A \) to be the \( \beta \)-tree defined by \( (t_A)_B = t_{(A_B)} \).
  This derivative map is functorial: for any paths \( A : \alpha \tpath \beta \) and \( B : \beta \tpath \gamma \), we have \( t_{(A_B)} = (t_A)_B \).
  If \( \tau \) has a group structure, then so does its type of trees: \( (t \cdot u)_A = t_A \cdot u_A \) and \( (t^{-1})_A = (t_A)^{-1} \).
  If \( \tau \) acts on \( \upsilon \), then \( \alpha \)-trees of \( \tau \) act on \( \alpha \)-trees of \( \upsilon \): \( (t(u))_A = t_A(u_A) \).

  If \( \#\tau \leq \#\mu \), there are at most \( \#\mu \)-many \( \alpha \)-trees of \( \tau \), since there are less than \( \cof(\ord(\#\mu)) \)-many \( \alpha \)-extended indices, allowing us to conclude by \cref{prop:card_subset_card_lt_cof} as each such tree is a subset of \( (\alpha \tpath \bot) \times \tau \) of size less than \( \cof(\ord(\#\mu)) \).
  If \( \#\tau < \#\mu \), there are less than \( \#\mu \)-many \( \alpha \)-trees of \( \tau \), since there are less than \( \cof(\ord(\#\mu)) \)-many \( \alpha \)-extended indices and strong limits are closed under exponentials.
\end{definition}
\begin{definition}[structural permutation]
  \label{def:StrPerm}
  \uses{def:BasePerm,def:Tree}
  \lean{ConNF.StrPerm}
  \leanok
  Let \( \alpha \) be a type index.
  Then an \emph{\( \alpha \)-structural permutation} (or just \emph{\( \alpha \)-permutation}) is an \( \alpha \)-tree of base permutations.
  The type of \( \alpha \)-permutations is written \( \StrPerm_\alpha \).
\end{definition}
As an implementation detail, we create a typeclass \( \texttt{StrPermClass}_\alpha \) for permutations that `act like' \( \alpha \)-permutations: they have a group structure and a canonical group embedding into \( \StrPerm_\alpha \).
When we quantify over structural permutations in this paper, it should be formalised using an additional quantification over \( \texttt{StrPermClass}_\alpha \).
\begin{definition}[enumeration]
  \label{def:Enumeration}
  \uses{def:Small}
  \lean{ConNF.Enumeration}
  \leanok
  Let \( \tau \) be a type.
  An \emph{enumeration} of \( \tau \) is a pair \( E = (i, f) \) where \( i : \kappa \) and \( f \) is a partial function \( \kappa \to \tau \), such that all domain elements of \( f \) are strictly less than \( i \).\footnote{This should be encoded as a coinjective relation \( \kappa \to \tau \to \Prop \); see \cref{def:relation_props}.}
  If \( x : \tau \), we write \( x \in E \) for \( x \in \ran f \).
  The set \( \{ y \mid y \in E \} \), which we may also loosely call \( E \), is small.
  We will write \( \varnothing \) for the empty enumeration \( (0, \varnothing) \).

  If \( g : \tau \to \sigma \), then \( g \) lifts to a direct image function mapping enumerations of \( \tau \) to enumerations of \( \sigma \):
  \[ g(i, f) = (i, f');\quad f' = \{ (j, g(x)) \mid (j, x) \in f \} \]
  Thus, \( x \in g(E) \leftrightarrow x \in g[E] \).
  In the same way, groups that act on \( \tau \) also act on enumerations of \( \tau \).\footnote{Actually, we should probably implement this using the inverse image not the direct image for better definitional equalities.}
  If \( g : \sigma \to \tau \) is injective, then \( g \) lifts to an inverse image function mapping enumerations of \( \tau \) to enumerations of \( \sigma \):
  \[ g^{-1}(i, f) = (i, f');\quad f' = \{ (j, x) \mid (j, g(x)) \in f \} \]
  This operation may cause the domain of \( f \) to shrink, but we will keep \( i \) the same.

  If \( E = (i, e) \) and \( F = (j, f) \) are enumerations of \( \tau \), we define their \emph{concatenation} by
  \[ E + F = (i + j, e \cup f');\quad f' = \{(i + k, x) \mid (k, x) \in f \} \]
  This operation commutes with the others: \( x \in E + F \leftrightarrow x \in E \vee x \in F \), \( g[E + F] = g[E] + g[F] \), and \( g^{-1}[E + F] = g^{-1}[E] + g^{-1}[F] \).

  We define a partial order on enumerations by setting \( (i, e) \leq (j, f) \) if and only if \( f \) extends \( e \) as a partial function.
  We obtain various corollaries, such as \( E \leq F \to g(E) \leq g(F) \) and \( E \leq E + F \).

  Every small subset of \( \tau \) is the range of some enumeration of \( \tau \).

  If \( \#\tau \leq \#\mu \), then there are at most \( \#\mu \)-many enumerations of \( \tau \): enumerations are determined by an element of \( \kappa \) and a small subset of \( \kappa \times \tau \).
  If \( \#\tau < \#\mu \), then there are strictly less than \( \#\mu \)-many enumerations of \( \tau \): use the same reasoning and apply \cref{prop:card_subset_card_lt_cof}.
\end{definition}
\begin{definition}[base support]
  \label{def:BaseSupport}
  \uses{def:Enumeration,def:NearLitter}
  \lean{ConNF.BaseSupport}
  \leanok
  A \emph{base support} is a pair \( S = (S^\Atom, S^\NearLitter) \) where \( S^\Atom \) is an enumeration of atoms and \( S^\NearLitter \) is an enumeration of near-litters.
  There are precisely \( \#\mu \) base supports.
\end{definition}
\begin{definition}[structural support]
  \label{def:StrSupport}
  \uses{def:BaseSupport,def:StrPerm}
  \lean{ConNF.Support}
  \leanok
  A \emph{\( \beta \)-structural support} (or just \emph{\( \beta \)-support}) is a pair \( S = (S^\Atom, S^\NearLitter) \) where \( S^\Atom \) is an enumeration of \( (\beta \tpath \bot) \times \Atom \) and \( S^\NearLitter \) is an enumeration of \( (\beta \tpath \bot) \times \NearLitter \).
  The type of \( \beta \)-supports is written \( \StrSupp_\beta \).
  There are precisely \( \#\mu \) structural supports for any type index \( \beta \).

  For a path \( A : \beta \tpath \bot \), we write \( S_A \) for the base support \( T \) given by
  \[ T^\Atom = \{ (i, a) \mid (i, (A, a)) \in S^\Atom \};\quad T^\NearLitter = \{ (i, N) \mid (i, (A, N)) \in S^\NearLitter \} \]
  More generally, for a path \( A : \beta \tpath \gamma \), we write \( S_A \) for the \( \gamma \)-support \( T \) given by
  \[ T^\Atom = \{ (i, (B, a)) \mid (i, (A_B, a)) \in S^\Atom \};\quad T^\NearLitter = \{ (i, (B, N)) \mid (i, (A_B, N)) \in S^\NearLitter \} \]
  For a path \( A : \alpha \tpath \beta \), we write \( S^A \) for the \( \alpha \)-support \( T \) given by
  \[ T^\Atom = \{ (i, (A_B, a)) \mid (i, (B, a)) \in S^\Atom \};\quad T^\NearLitter = \{ (i, (A_B, N)) \mid (i, (B, N)) \in S^\NearLitter \} \]
  Clearly, \( (S^A)_A = S \).

  \( \beta \)-structural permutations act on pairs \( (A, x) \) by \( \pi(A, x) = (A, \pi_A(x)) \), where \( x \) is either an atom or a near-litter.
  Hence, structural permutations act on structural supports.

  Let \( \tau \) be a type, and let \( G \) be a \( \texttt{StrPermClass}_\beta \)-group that acts on \( \tau \).
  We say that \( S \) \emph{supports} \( x : \tau \) under the action of \( G \) if whenever \( \pi : G \) fixes \( S \), it also fixes \( x \), and moreover, if \( \beta = \bot \) then \( S_A^\NearLitter \) is empty for any \( A : \bot \tpath \bot \) (and of course there is exactly one such path).
\end{definition}
\begin{definition}[structural set]
  \label{def:StrSet}
  \uses{def:StrPerm}
  \lean{ConNF.StrSet}
  \leanok
  The type of \emph{\( \alpha \)-structural sets}, denoted \( \StrSet_\alpha \), is defined by well-founded recursion on \( \lambda^\bot \).
  \begin{itemize}
    \item \( \StrSet_\bot \coloneq \Atom \);
    \item \( \StrSet_\alpha \coloneq \prod_{\beta : \lambda^\bot} \beta < \alpha \to \Set \StrSet_\beta \) where \( \alpha : \lambda \).
  \end{itemize}
  These equalities will in fact only be equivalences in the formalisation.
  We define the action of \( \alpha \)-permutations (more precisely, inhabitants of some type with a \( \texttt{StrPermClass}_\alpha \) instance) on \( \alpha \)-structural sets by well-founded recursion.
  \begin{itemize}
    \item \( \pi(x) = \pi_{\nil(\bot)}(x) \) if \( \alpha \equiv \bot \);
    \item \( \pi(x) = (\beta, h \mapsto \pi_h[x(\beta, h)]) \) if \( \alpha : \lambda \).
  \end{itemize}
\end{definition}

\section{Position functions}
\begin{definition}[position function]
  \label{def:Position}
  \uses{def:Params}
  \lean{ConNF.Position}
  \leanok
  Let \( \tau \) be a type.
  A \emph{position function} for \( \tau \) is an injection \( \iota : \tau \to \mu \).
  This is a typeclass.
\end{definition}
\begin{proposition}[injective functions from denied sets]
  \label{prop:funOfDeny}
  \uses{def:Params}
  \lean{ConNF.funOfDeny}
  \leanok
  Let \( \tau \) be a type such that \( \#\tau \leq \#\mu \).
  Let \( D : \tau \to \Set(\mu) \) be a function such that for each \( x : \tau \), the set \( D(x) \), called the \emph{denied set} of \( x \), has size less than \( \cof(\ord(\#\mu)) \).
  Then there is an injective function \( f : \tau \to \mu \) such that if \( \nu \in D(x) \), then \( \nu < f(x) \).
\end{proposition}
\begin{proof}
  \leanok
  Pick a well-ordering \( \prec \) of \( \tau \) of length at most \( \ord(\#\mu) \).
  Define \( f \) by well-founded recursion on \( \prec \).
  Suppose that we have already defined \( f \) for all \( y \prec x \).
  Then let
  \[ X = \{ f(y) \mid y \prec x \} \cup \{ \nu \mid \exists \nu' \in D(x),\, \nu \leq \nu' \} \]
  This set has size strictly less than \( \mu \), so there is some \( \nu : \mu \) not contained in it.
  Set \( f(x) = \nu \).
\end{proof}
\begin{proposition}[base positions]
  \label{prop:BasePositions}
  \uses{def:Position}
  \leanok
  There are position functions on \( \Atom, \NearLitter \) that are jointly injective and satisfy
  \begin{itemize}
    \item \( \iota(\NL(a^\circ)) < \iota(a) \) for every atom \( a \);
    \item \( \iota(\NL(N^\circ)) \leq \iota(N) \) for every near-litter \( N \);
    \item \( \iota(a) < \iota(N) \) for every near-litter \( N \) and atom \( a \in N \symmdiff \LS(N^\circ) \).\footnote{TODO: Make syntax for \( N \symmdiff \LS(N^\circ) \).}
  \end{itemize}
  We register these position functions as instances for use in typeclass inference.
  We also define \( \iota(L) = \iota(\NL(L)) \) for litters.
\end{proposition}
\begin{proof}
  \uses{prop:funOfDeny}
  \leanok
  First, establish an equivalence \( f_\Litter : \Litter \simeq \mu \).
  Use \cref{prop:funOfDeny} to obtain an injective map \( f_\Atom : \NearLitter \to \mu \) such that \( f_\Litter(a^\circ) < f_\Atom(a) \) for each atom \( a \).
  Now use \cref{prop:funOfDeny} again to obtain an injective map \( f_\NearLitter : \NearLitter \to \mu \) such that
  \[ f_\Litter(N^\circ) < f_\NearLitter(N);\quad f_\Atom(a) < f_\NearLitter(N) \text{ for } a \in N \symmdiff \LS(N^\circ) \]
  Endow \( 3 \times \mu \) with its lexicographic order, of order type \( \ord(\#\mu) \), giving an order isomorphism \( e : 3 \times \mu \simeq \mu \).
  Finally, we define
  \[ \iota(a) = e(1, f_\Atom(a));\quad \iota(N) = \begin{cases}
    e(0, f_\Litter(N^\circ)) & \text{if } N = \NL(N^\circ) \\
    e(2, f_\NearLitter(N)) & \text{otherwise}
  \end{cases} \]
\end{proof}

\section{Hypotheses of the recursion}
\begin{definition}[model data]
  \label{def:ModelData}
  \uses{def:StrSupport,def:StrSet}
  \lean{ConNF.ModelData}
  \leanok
  Let \( \alpha \) be a type index.
  \emph{Model data} at type \( \alpha \) consists of:\footnote{A type theory problem with \texttt{export}ing this data is that under different assumptions, things like different spellings of \( \TSet_\alpha \) might require case splitting on \( \alpha \) before they become defeq (e.g.\ see the old version of \texttt{Model/FOA.lean}). There doesn't seem to be an easy way around this.}
  \begin{itemize}
    \item a \( \TSet_\alpha \) called the type of \emph{tangled sets} or \emph{t-sets}, which will be our type of model elements at level \( \alpha \), with an embedding \( U_\alpha : \TSet_\alpha \to \StrSet_\alpha \);
    \item a group \( \AllPerm_\alpha \) called the type of \emph{allowable permutations}, with a \( \texttt{StrPermClass}_\alpha \) instance and a specified action on \( \TSet_\alpha \),
  \end{itemize}
  such that
  \begin{itemize}
    \item if \( \rho : \AllPerm_\alpha \) and \( x : \TSet_\alpha \), then \( \rho(U_\alpha(x)) = U_\alpha(\rho(x)) \);
    \item every t-set of type \( \alpha \) has an \( \alpha \)-support (\cref{def:StrSupport}) for its action under the \( \alpha \)-allowable permutations.
  \end{itemize}
\end{definition}
\begin{definition}[tangle]
  \label{def:Tangle}
  \uses{def:ModelData}
  \lean{ConNF.Tangle}
  \leanok
  Let \( \alpha \) be a type index with model data.
  An \emph{\( \alpha \)-tangle} is a pair \( t = (x, S) \) where \( x \) is a tangled set of type \( \alpha \) and \( S \) is an \( \alpha \)-support for \( x \).
  We define \( \set(t) = x \) and \( \supp(t) = S \).
  The type of \( \alpha \)-tangles is denoted \( \Tang_\alpha \).
  Allowable permutations \( \rho \) act on tangles by \( \rho((x, S)) = (\rho(x), \rho(S)) \), and so \( \supp(t) \) supports \( t \) for its action under the allowable permutations.
  Therefore, each tangled set \( x \) is of the form \( \set(t) \) for some tangle \( t \).
\end{definition}
\begin{proposition}[fuzz maps]
  \label{prop:fuzz}
  \uses{def:Tangle,def:Position}
  \lean{ConNF.fuzz}
  \leanok
  Let \( \beta \) be a type index with model data, and suppose that \( \Tang_\beta \) has a position function.
  Let \( \gamma \) be any proper type index not equal to \( \beta \).
  Then there is an injective \emph{fuzz map} \( f_{\beta,\gamma} : \Tang_\beta \to \Litter \) such that \( \iota(t) < \iota(f_{\beta,\gamma}(t)) \), and the different \( f_{\beta,\gamma} \) all have disjoint ranges.
  In particular, for any near-litter \( N \) with \( N^\circ = f_{\beta,\gamma}(t) \), we have \( \iota(t) < \iota(N) \), and additionally, for any atom \( a \) with \( a^\circ = f_{\beta,\gamma}(t) \), we have \( \iota(t) < \iota(a) \).\footnote{We might want to encapsulate atoms and near-litters somehow. We could make a typeclass, or write theorems in terms of the coproduct \( \Atom \oplus \NearLitter \).}
\end{proposition}
\begin{proof}
  \uses{prop:funOfDeny}
  \leanok
  We define \( g : \Tang_\beta \to \mu \) by \cref{prop:funOfDeny}, where the denied sets are given by \( D(t) = \{ \iota(t) \} \).
  Then we set \( f_{\beta,\gamma}(t) = (g(t), \beta, \gamma) \).
\end{proof}
\begin{definition}[inflexible path]
  \label{def:InflexiblePath}
  \uses{prop:fuzz}
  \lean{ConNF.InflexiblePath}
  \leanok
  Let \( \alpha \) be a proper type index.
  Suppose that we have model data for all type indices \( \beta \leq \alpha \) and position functions for \( \Tang_\beta \) for all \( \beta < \alpha \).
  For any type index \( \beta \leq \alpha \), a \emph{inflexible \( \beta \)-path} is a tuple \( I = (\gamma, \delta, \varepsilon, A) \) where \( \delta, \varepsilon < \gamma \) are distinct, the index \( \varepsilon \) is proper, and \( A : \beta \tpath \gamma \).
  We will write \( \gamma_I, \delta_I, \varepsilon_I, A_I \) for its fields.
  Inflexible paths have a coderivative operation, given by \( (\gamma, \delta, \varepsilon, A)^B = (\gamma, \delta, \varepsilon, A^B) \).
\end{definition}
\begin{definition}[typed near-litter]
  \label{def:TypedNearLitter}
  \uses{def:ModelData,def:Tangle,prop:BasePositions}
  \lean{ConNF.TypedNearLitters}
  \leanok
  Let \( \alpha \) be a proper type index with model data, and suppose that \( \Tang_\alpha \) has a position function.
  We say that \( \alpha \) has \emph{typed near-litters} if there is an embedding \( \typed_\alpha : \NearLitter \to \TSet_\alpha \) such that
  \begin{itemize}
    \item if \( \rho : \AllPerm_\alpha \) and \( N : \NearLitter \), then \( \rho(\typed_\alpha(N)) = \typed_\alpha(\rho_\bot(N)) \); and
    \item if \( N \) is a near-litter and \( t \) is an \( \alpha \)-tangle such that \( \set(t) = \typed_\alpha(N) \), we have \( \iota(N) \leq \iota(t) \).
  \end{itemize}
  Objects of the form \( \typed_\alpha \) are called \emph{typed near-litters}.
\end{definition}
\begin{definition}[coherent data]
  \label{def:CoherentData}
  \uses{def:TypedNearLitter,def:InflexiblePath}
  \lean{ConNF.CoherentData}
  \leanok
  Let \( \alpha \) be a proper type index.
  Suppose that we have model data for all type indices \( \beta \leq \alpha \), position functions for \( \Tang_\beta \) for all \( \beta < \alpha \), and typed near-litters for all \( \beta < \alpha \).
  We say that the model data is \emph{coherent} below level \( \alpha \) if the following hold.
  \begin{itemize}
    \item For \( \gamma < \beta \leq \alpha \), there is a map \( \AllPerm_\beta \to \AllPerm_\gamma \) that commutes with the coercions from \( \AllPerm_{(-)} \) to \( \StrPerm_{(-)} \).
    We can use this map to define arbitrary derivatives of allowable permutations by recursion on paths.
    \item If \( (x, S) \) is a \( \beta \)-tangle for \( \beta < \alpha \), and \( y \) is an atom or near-litter that occurs in the range of \( S_A \), then \( \iota(y) < \iota(x, S) \).
    \item Let \( \beta \leq \alpha \), and let \( \gamma, \delta < \beta \) be distinct with \( \delta \) proper.
    Let \( t : \Tang_\gamma \) and \( \rho : \AllPerm_\beta \).
    Then
    \[ (\rho_\delta)_\bot(f_{\gamma,\delta}(t)) = f_{\gamma,\delta}(\rho_\gamma(t)) \]
    In particular, for every \( \beta \leq \alpha \), \( \beta \)-allowable permutation \( \rho \), and \( \beta \)-inflexible path \( I \), we obtain
    \[ ((\rho_A)_\varepsilon)_\bot(f_{\delta,\varepsilon}(t)) = f_{\delta,\varepsilon}((\rho_A)_\delta(t)) \]
    where subscripts of \( I \) are suppressed.
    \item Suppose that \( \beta \leq \alpha \) and \( (\rho(\gamma))_{\gamma < \beta} \) is a collection of allowable permutations such that whenever \( \gamma, \delta < \beta \) are distinct, \( \delta \) is proper, and \( t : \Tang_\delta \), we have
    \[ (\rho(\delta))_\bot(f_{\gamma,\delta}(t)) = f_{\gamma,\delta}(\rho(\gamma)(t)) \]
    Then there is a \( \beta \)-allowable permutation \( \rho \) with \( \rho_\gamma = \rho(\gamma) \) for each \( \gamma < \beta \).
    \item If \( \beta \leq \alpha \) is a proper type index and \( x : \TSet_\beta \), then for any \( \gamma < \beta \),
    \[ U_\beta(x)(\gamma) \subseteq \ran U_\gamma \]
    \item (extensionality) If \( \beta, \gamma \leq \alpha \) are proper type indices where \( \gamma < \beta \), the map \( U_\beta(-)(\gamma) : \TSet_\beta \to \Set \StrSet_\gamma \) is injective.
    \item If \( \beta, \gamma : \lambda \) where \( \gamma < \beta \), for every \( x : \TSet_\gamma \) there is some \( y : \TSet_\beta \) such that \( U_\beta(y)(\gamma) = \{ x \} \).
    We write \( \singleton_\beta(x) \) for this object \( y \), which is uniquely defined by extensionality.
  \end{itemize}
  Note that this structure contains data (the derivative maps for allowable permutations and the singleton operations), but the type is a subsingleton: any two inhabitants are propositionally equal.
  We will not use this fact directly, but the idea will have relevance in \cref{c:induction}.
\end{definition}
The strategy of our construction is as follows.
\begin{itemize}
  \item In \cref{c:construction}, we assume model data, position functions, and typed near-litters for all types \( \beta < \alpha \), and construct model data at level \( \alpha \).
  \item In \cref{c:foa,c:counting}, we assume coherent data below level \( \alpha \) (along with the assumptions required for this definition to make sense) and prove that \( \#\TSet_\alpha = \#\mu \).
  \item In \cref{c:induction}, we use the results of \cref{c:construction,c:foa,c:counting} to show that we can provide position functions and typed near-litters at level \( \alpha \).
  We then show that these constructions may be iterated so that we may define all of the above structures at every proper type level.
\end{itemize}
